---
title: "Trisha_Script"
author: "Trisha Henderson"
date: "2024-03-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr) #needed for the %>% function in the data subset loops
library(ggplot2)
#install.packages("GGally")
library("GGally")
library(knitr)
library(xtable)
#install.packages("jtools")
library("jtools")
#install.packages("devtools")
#install.packages("stargazer")
library(stargazer)
#install.packages("caret")
library(lattice)
library(caret)
```

## R Markdown

```{r}
diagnosing_AD_data <- read_csv("diagnosing_AD_data.csv", show_col_types = FALSE) %>%
  mutate(class = case_when(class == "H" ~ 0,
                           class == "P" ~ 1))
```


```{r}

task1 <- diagnosing_AD_data %>%
  select(ends_with("e1"), ends_with("x1"), ends_with("r1"), ends_with("n1"), ends_with("t1"))

task2 <- diagnosing_AD_data %>%
  select(ends_with("e2"), ends_with("x2"), ends_with("r2"), ends_with("n2"), ends_with("t2"))

task3 <- diagnosing_AD_data %>%
  select(ends_with("e3"), ends_with("x3"), ends_with("r3"), ends_with("n3"), ends_with("t3"))

task4 <- diagnosing_AD_data %>%
  select(ends_with("e4"), ends_with("x4"), ends_with("r4"), ends_with("n4"), ends_with("t4"))

task5 <- diagnosing_AD_data %>%
  select(ends_with("e5"), ends_with("x5"), ends_with("r5"), ends_with("n5"), ends_with("t5"))

task6 <- diagnosing_AD_data %>%
  select(ends_with("e6"), ends_with("x6"), ends_with("r6"), ends_with("n6"), ends_with("t6"))

task7 <- diagnosing_AD_data %>%
  select(ends_with("e7"), ends_with("x7"), ends_with("r7"), ends_with("n7"), ends_with("t7"))

task8 <- diagnosing_AD_data %>%
  select(ends_with("e8"), ends_with("x8"), ends_with("r8"), ends_with("n8"), ends_with("t8"))

task9 <- diagnosing_AD_data %>%
  select(ends_with("e9"), ends_with("x9"), ends_with("r9"), ends_with("n9"), ends_with("t9"))

task10 <- diagnosing_AD_data %>%
  select(ends_with("10"))

task11 <- diagnosing_AD_data %>%
  select(ends_with("11"))

task12 <- diagnosing_AD_data %>%
  select(ends_with("12"))

task13 <- diagnosing_AD_data %>%
  select(ends_with("13"))

task14 <- diagnosing_AD_data %>%
  select(ends_with("14"))

task15 <- diagnosing_AD_data %>%
  select(ends_with("15"))

task16 <- diagnosing_AD_data %>%
  select(ends_with("16"))

task17 <- diagnosing_AD_data %>%
  select(ends_with("17"))

task18 <- diagnosing_AD_data %>%
  select(ends_with("18"))

task19 <- diagnosing_AD_data %>%
  select(ends_with("19"))

task20 <- diagnosing_AD_data %>%
  select(ends_with("20"))

task21 <- diagnosing_AD_data %>%
  select(ends_with("21"))

task22 <- diagnosing_AD_data %>%
  select(ends_with("22"))

task23 <- diagnosing_AD_data %>%
  select(ends_with("23"))

task24 <- diagnosing_AD_data %>%
  select(ends_with("24"))

task25 <- diagnosing_AD_data %>%
  select(ends_with("25"))


```

```{r}
H <- which(diagnosing_AD_data$class == "0") 
P <- which(diagnosing_AD_data$class == "1")

n_train_H <- ceiling(0.8 * length(H))
n_train_P <- ceiling(0.8 * length(P))

train_H <- sample(H, size = n_train_H)
train_P <- sample(P, size = n_train_P)

train_both <- c(train_H, train_P)
test <- diagnosing_AD_data[-train_both, ]
diagnosing_AD_data <- diagnosing_AD_data[train_both, ]
```

\hstart
the above is showing the 25 different tasks, using the full data set. the first 9 tasks have additional 'ends with' sections because if not, tasks from 11 and 21 would mix in with them. I used a minimal amount of additions to act as catch alls, to reduce coding time
\hstop

```{r}
ggpairs(task1)
```



```{r}
smalldata <- diagnosing_AD_data %>%
  select(starts_with("air"), starts_with("disp"), starts_with("max_x"), starts_with("max_y"), starts_with("num"), starts_with("paper"), starts_with("total"), starts_with("class"))
```

\hstart
this is the small data, that is showing only the 7 tasks we chose that can be considered accessible. 
\hstop

```{r}

t1 <- smalldata %>%
  select(ends_with("e1"), ends_with("x1"), ends_with("n1"))

t2 <- smalldata %>%
  select(ends_with("e2"), ends_with("x2"), ends_with("n2"))

t3 <- smalldata %>%
  select(ends_with("e3"), ends_with("x3"), ends_with("n3"))

t4 <- smalldata %>%
  select(ends_with("e4"), ends_with("x4"), ends_with("n4"))

t5 <- smalldata %>%
  select(ends_with("e5"), ends_with("x5"), ends_with("n5"))

t6 <- smalldata %>%
  select(ends_with("e6"), ends_with("x6"), ends_with("n6"))

t7 <- smalldata %>%
  select(ends_with("e7"), ends_with("x7"), ends_with("n7"))

t8 <- smalldata %>%
  select(ends_with("e8"), ends_with("x8"), ends_with("n8"))

t9 <- smalldata %>%
  select(ends_with("e9"), ends_with("x9"), ends_with("n9"))

t10 <- smalldata %>%
  select(ends_with("10"))

t11 <- smalldata %>%
  select(ends_with("11"))

t12 <- smalldata %>%
  select(ends_with("12"))

t13 <- smalldata %>%
  select(ends_with("13"))

t14 <- smalldata %>%
  select(ends_with("14"))

t15 <- smalldata %>%
  select(ends_with("15"))

t16 <- smalldata %>%
  select(ends_with("16"))

t17 <- smalldata %>%
  select(ends_with("17"))

t18 <- smalldata %>%
  select(ends_with("18"))

t19 <- smalldata %>%
  select(ends_with("19"))

t20 <- smalldata %>%
  select(ends_with("20"))

t21 <- smalldata %>%
  select(ends_with("21"))

t22 <- smalldata %>%
  select(ends_with("22"))

t23 <- smalldata %>%
  select(ends_with("23"))

t24 <- smalldata %>%
  select(ends_with("24"))

t25 <- smalldata %>%
  select(ends_with("25"))

```


\hstart
this is the small data tasks that we can use for the pairs plots
\hstop

```{r}
pairs(t1) + title("Task 1 Features")
pairs(t2) 
pairs(t3)
pairs(t4)
pairs(t5)
pairs(t6)
pairs(t7)
pairs(t8)
pairs(t9)
pairs(t10)
pairs(t11)
pairs(t12)
pairs(t13)
```

\hstart
1st half of the pairs plots for the small data
\hstop

```{r}
pairs(t14)
pairs(t15)
pairs(t16)
pairs(t17)
pairs(t18)
pairs(t19)
pairs(t20)
pairs(t21)
pairs(t22)
pairs(t23)
pairs(t24)
pairs(t25)
```

\hstart
2nd half of the pairs plots for the small data
\hstop

```{r}
ggpairs(t1, progress = FALSE)
ggpairs(t2, progress = FALSE)
ggpairs(t3, progress = FALSE)
ggpairs(t4, progress = FALSE)
ggpairs(t5, progress = FALSE)
ggpairs(t6, progress = FALSE)
ggpairs(t7, progress = FALSE)
ggpairs(t8, progress = FALSE)
ggpairs(t9, progress = FALSE)
ggpairs(t10, progress = FALSE)
ggpairs(t11, progress = FALSE)
ggpairs(t12, progress = FALSE)
ggpairs(t13, progress = FALSE)
```

\hstart
NICE VERSION of 1st half of the pairs plots for the small data
\hstop

```{r}
ggpairs(t14, progress = FALSE)
ggpairs(t15, progress = FALSE)
ggpairs(t16, progress = FALSE)
ggpairs(t17, progress = FALSE)
ggpairs(t18, progress = FALSE)
ggpairs(t19, progress = FALSE)
ggpairs(t20, progress = FALSE)
ggpairs(t21, progress = FALSE)
ggpairs(t22, progress = FALSE)
ggpairs(t23, progress = FALSE)
ggpairs(t24, progress = FALSE)
ggpairs(t25, progress = FALSE)
```

\hstart
NICE VERSION of 2nd half of the pairs plots for the small data
\hstop

```{r}
g1 <- glm(class ~ air_time1 + paper_time1 + disp_index1 + max_x_extension1 + max_y_extension1 + num_of_pendown1, data = diagnosing_AD_data, family=binomial(link="logit"))
g1


g2 <- glm(class ~ air_time2 + paper_time2 + disp_index2 + max_x_extension2 + max_y_extension2 + num_of_pendown2, data = diagnosing_AD_data, family=binomial(link="logit"))

print(summ(g2,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))

stargazer(g2, type="latex",
          dep.var.labels=c("Miles/(US) gallon","Fast car (=1)"),
          covariate.labels=c("Gross horsepower","Rear axle ratio","Four foward
                             gears", "Five forward gears","Type of transmission
                             (manual=1)"), out="models.htm")

```

\hstart
logistic regression model START
\hstop


```{r mylatextable, results = "asis"}
stargazer(g2, type = 'text', out='foo.html', title="Logistic Regression Results for Task 2 Model",covariate.labels=c("Air Time","Paper Time",
"Dispersment Index","Maximum X Extension","Maximum Y Extension","Number of Pendowns"), dep.var.labels=c("Class"), no.space=TRUE, single.row=TRUE)

stargazer(g15, type = 'text', out='foo15.html', title="Logistic Regression Results for Task 15 Model",covariate.labels=c("Air Time","Paper Time","Maximum X Extension","Maximum Y Extension","Number of Pendowns"), dep.var.labels=c("Class"), no.space=TRUE, single.row=TRUE)



g15 <- glm(class ~ air_time15 + paper_time15 + max_x_extension15 + max_y_extension15 + num_of_pendown15, data = diagnosing_AD_data, family=binomial(link="logit"))
```


\hstart
1st attempt for small data task1
\hstop


```{r}
g1 <- glm(class ~ air_time1 + paper_time1 + max_x_extension1 + max_y_extension1 + num_of_pendown1, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g1,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g1)

g2 <- glm(class ~ air_time2 + paper_time2 + max_x_extension2 + max_y_extension2 + num_of_pendown2, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g2,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g2)

g3 <- glm(class ~ air_time3 + paper_time3 + max_x_extension3 + max_y_extension3 + num_of_pendown3, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g3,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g3)

g4 <- glm(class ~ air_time4 + paper_time4  + max_x_extension4 + max_y_extension4 + num_of_pendown4, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g4,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g4)

g5 <- glm(class ~ air_time5 + paper_time5  + max_x_extension5 + max_y_extension5 + num_of_pendown5, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g5,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g5)
```


\hstart
will be using small data for logistic regression - log reg tasks 1 to 5
\hstop


```{r}
g6 <- glm(class ~ air_time6 + paper_time6  + max_x_extension6 + max_y_extension6 + num_of_pendown6, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g6,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g6)

g7 <- glm(class ~ air_time7 + paper_time7  + max_x_extension7 + max_y_extension7 + num_of_pendown7, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g7,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g7)

g8 <- glm(class ~ air_time8 + paper_time8  + max_x_extension8 + max_y_extension8 + num_of_pendown8, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g8,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g8)

g9 <- glm(class ~ air_time9 + paper_time9 + max_x_extension9 + max_y_extension9 + num_of_pendown9, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g9,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g9)

g10 <- glm(class ~ air_time10 + paper_time10  + max_x_extension10 + max_y_extension10 + num_of_pendown10, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g10,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g10)
```

\hstart
will be using small data for logistic regression - log reg tasks 6 to 10
\hstop


```{r}
g11 <- glm(class ~ air_time11 + paper_time11 + max_x_extension11 + max_y_extension11 + num_of_pendown11, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g11,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g11)

g12 <- glm(class ~ air_time12 + paper_time12 + max_x_extension12 + max_y_extension12 + num_of_pendown12, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g12,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g12)

g13 <- glm(class ~ air_time13 + paper_time13 + max_x_extension13 + max_y_extension13 + num_of_pendown13, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g13,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g13)

g14 <- glm(class ~ air_time14 + paper_time14 + max_x_extension14 + max_y_extension14 + num_of_pendown14, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g14,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g14)

g15 <- glm(class ~ air_time15 + paper_time15 + max_x_extension15 + max_y_extension15 + num_of_pendown15, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g15,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g15)
```

\hstart
will be using small data for logistic regression - log reg tasks 11 to 15
\hstop



```{r}
g16 <- glm(class ~ air_time16 + paper_time16 + max_x_extension16 + max_y_extension16 + num_of_pendown16, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g16,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g16)

g17 <- glm(class ~ air_time17 + paper_time17 + max_x_extension17 + max_y_extension17 + num_of_pendown17, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g17,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g17)

g18 <- glm(class ~ air_time18 + paper_time18 + max_x_extension18 + max_y_extension18 + num_of_pendown18, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g18,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g18)

g19 <- glm(class ~ air_time19 + paper_time19 + max_x_extension19 + max_y_extension19 + num_of_pendown19, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g19,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g19)

g20 <- glm(class ~ air_time20 + paper_time20 + max_x_extension20 + max_y_extension20 + num_of_pendown20, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g20,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g20)
```

\hstart
will be using small data for logistic regression - log reg tasks 16 to 20
\hstop


```{r}
g21 <- glm(class ~ air_time21 + paper_time21 + max_x_extension21 + max_y_extension21 + num_of_pendown21, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g21,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g21)

g22 <- glm(class ~ air_time22 + paper_time22 + max_x_extension22 + max_y_extension22 + num_of_pendown22, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g22,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g22)

g23 <- glm(class ~ air_time23 + paper_time23 + max_x_extension23 + max_y_extension23 + num_of_pendown23, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g23,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g23)

g24 <- glm(class ~ air_time24 + paper_time24 + max_x_extension24 + max_y_extension24 + num_of_pendown24, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g24,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g24)

g25 <- glm(class ~ air_time25 + paper_time25 + max_x_extension25 + max_y_extension25 + num_of_pendown25, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g25,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g25)
```

\hstart
will be using small data for logistic regression - log reg tasks 20 to 25
\hstop


```{r}
logLik(g1)
logLik(g2)
logLik(g3)
logLik(g4)
logLik(g5)
logLik(g6)
logLik(g7)
logLik(g8)
logLik(g9)
logLik(g10)
logLik(g11)
logLik(g12)
logLik(g13)
logLik(g14)
logLik(g15)
logLik(g16)
logLik(g17)
logLik(g18)
logLik(g19)
logLik(g20)
logLik(g21)
logLik(g22)
logLik(g23)
logLik(g24)
logLik(g25)
```

\hstart
mod 18 is worst (-109.1087); and mod 15 is BEST (-78.79616) - for AIC curve val
\hstop

```{r}
train <- subset(diagnosing_AD_data, select = -ID)
train_sub <- train[,1:17]
mean_sub <- apply(train_sub[,1:17], 2, mean)
sd_sub <- apply(train_sub[,1:17], 2, sd)
train_std <- matrix(rep(NA, nrow(train_sub) * ncol(train_sub)), nrow = nrow(train_sub))
for(i in 1:ncol(train_sub)) {
  train_std[,i] <- c(train_sub[,i] - mean_sub[i])[[1]]/sd_sub[i]
}
test1 <- as.data.frame(subset(test))
train_std <- as.data.frame(train_std)
colnames(train_std) <- colnames(train_sub)

```


```{r}
g1a <- glm(as.factor(train$class) ~ .,data = train_std, family=binomial(link="logit")) #uses centered and standardized
g1a_full <- glm(as.factor(train$class) ~ .,data = train_sub, family=binomial(link="logit"))
# subset the test set in a similar manner (so the first 17 columns), and then center and standardize the way we did above, then test the performance of both models (so the test set that's standardized on g1a and the original test set on g1a_full). if the two perform similarly, just go with the non-standardized
# try to add in variables one at a time until it no longer works
print(summ(g1a,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g1a)
#gmrtand grmt mean co linearity are doing same thing take out the overlaps while holding everything else constant.
pred1<-format(round(predict(g1a,test)))
conf <- confusionMatrix(pred1, as.factor(test$class))

```

```{r}
#test example demonstrating how to get probabilities from log odds

fitted_log_odds <- predict(g1a) #these are on log odds scale
fitted_odds <- exp(fitted_log_odds) #these are on odds scale
fitted_probabilities <- fitted_odds/(1+fitted_odds) #these are probabilities
confusionMatrix()
#feed these to the confusion matrix
```

```{r}
gta <- glm(as.factor(train$class) ~ ., data= train_std, family=binomial(link="logit"))
predgta <- predict(gta, test1, type="response")
pred_labsgta <- ifelse(pred1>0.5,1,0)
conf_matrixgta <- confusionMatrix(as.factor(pred_labsgta), as.factor(test$class))
print(conf_matrixgta)

```

