---
output: pdf_document
---
```{r packages}
library(readr)
full <- read_csv("diagnosing_AD_data.csv")
library(dplyr) #needed for the %>% function in the data subset loops
library(ggplot2)
```

```{r accessible subset}
a=1
b=6
c=15
access <- data.frame(matrix(nrow=174))

for (i in 1:25) {
  access <- access %>%
    mutate(full[a:(a+2)], full[b:(b+1)], full[c:(c+1)])
  
  a <- a+18
  b <- b+18
  c <- c+18
  
}

access <- access %>%
  mutate(full[451:452])

access <- subset(access, select = -(matrix.nrow...174.))
```

```{r task subsets}
d <- 2

for (i in (1:25)) {
  df <- data.frame(access[1], access[d:(d+6)])
  df <- df %>%
    mutate(access[177])
  
  assign( paste("Task", i, sep = "_"), df)
  d <- d+7
}

```

```{r demographics}
demographics <- data_frame("Class" = c("Patients", "Control Group"), "Age" = c(71.5, 68.9), "Education" = c(10.8, 12.9), "#Women" = c(46,51), "#Men" = c(44,39))
```

#Chat GPT output
## Dividing code (lines 236-252)
Dataset Initialization:

The dataset is read from a CSV file specified by dataset_path.
The first line of the CSV file is assumed to contain feature names, which are extracted and stored in features_names.
Dataset Splitting:

The dataset is split into features (X) and labels (Y).
X contains all the columns from the dataset except the last two, assuming the last two columns are the label and another identifier.
Y contains the labels, which are assumed to be the second-to-last column in the dataset.
Train-Test Split:

The train_test_split function from scikit-learn is used to split the dataset into training and testing sets.
x_train, x_test contain the feature data for the training and testing sets, respectively.
y_train, y_test contain the corresponding labels for the training and testing sets, respectively.
The test_size parameter determines the proportion of the dataset that will be used for testing. In this case, it's set to test_ratio, which is 0.2 (20% of the data).
Counter for Class Distribution:

counter_train and counter_test variables are used to count the occurrences of each class in the training and testing sets, respectively.
These counters provide insights into the distribution of classes in both sets.
Output Information:

Information about the dataset division, including the test ratio, random state, and counts of elements in the training and testing sets for each class, is printed and added to the report.
This dataset division process ensures that the dataset is appropriately split into training and testing sets, allowing for model training and evaluation while maintaining class distribution balance between the two sets.
