---
title: "Trisha_Script"
author: "Trisha Henderson"
date: "2024-03-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr) #needed for the %>% function in the data subset loops
library(ggplot2)
```

## R Markdown

```{r}
diagnosing_AD_data <- read_csv("diagnosing_AD_data.csv", show_col_types = FALSE)

task1 <- diagnosing_AD_data %>%
  select(ends_with("e1"), ends_with("x1"), ends_with("r1"), ends_with("n1"), ends_with("t1"))

task2 <- diagnosing_AD_data %>%
  select(ends_with("e2"), ends_with("x2"), ends_with("r2"), ends_with("n2"), ends_with("t2"))

task3 <- diagnosing_AD_data %>%
  select(ends_with("e3"), ends_with("x3"), ends_with("r3"), ends_with("n3"), ends_with("t3"))

task4 <- diagnosing_AD_data %>%
  select(ends_with("e4"), ends_with("x4"), ends_with("r4"), ends_with("n4"), ends_with("t4"))

task5 <- diagnosing_AD_data %>%
  select(ends_with("e5"), ends_with("x5"), ends_with("r5"), ends_with("n5"), ends_with("t5"))

task6 <- diagnosing_AD_data %>%
  select(ends_with("e6"), ends_with("x6"), ends_with("r6"), ends_with("n6"), ends_with("t6"))

task7 <- diagnosing_AD_data %>%
  select(ends_with("e7"), ends_with("x7"), ends_with("r7"), ends_with("n7"), ends_with("t7"))

task8 <- diagnosing_AD_data %>%
  select(ends_with("e8"), ends_with("x8"), ends_with("r8"), ends_with("n8"), ends_with("t8"))

task9 <- diagnosing_AD_data %>%
  select(ends_with("e9"), ends_with("x9"), ends_with("r9"), ends_with("n9"), ends_with("t9"))

task10 <- diagnosing_AD_data %>%
  select(ends_with("10"))

task11 <- diagnosing_AD_data %>%
  select(ends_with("11"))

task12 <- diagnosing_AD_data %>%
  select(ends_with("12"))

task13 <- diagnosing_AD_data %>%
  select(ends_with("13"))

task14 <- diagnosing_AD_data %>%
  select(ends_with("14"))

task15 <- diagnosing_AD_data %>%
  select(ends_with("15"))

task16 <- diagnosing_AD_data %>%
  select(ends_with("16"))

task17 <- diagnosing_AD_data %>%
  select(ends_with("17"))

task18 <- diagnosing_AD_data %>%
  select(ends_with("18"))

task19 <- diagnosing_AD_data %>%
  select(ends_with("19"))

task20 <- diagnosing_AD_data %>%
  select(ends_with("20"))

task21 <- diagnosing_AD_data %>%
  select(ends_with("21"))

task22 <- diagnosing_AD_data %>%
  select(ends_with("22"))

task23 <- diagnosing_AD_data %>%
  select(ends_with("23"))

task24 <- diagnosing_AD_data %>%
  select(ends_with("24"))

task25 <- diagnosing_AD_data %>%
  select(ends_with("25"))

```

\hstart
the above is showing the 25 different tasks, using the full data set. the first 9 tasks have additional 'ends with' sections because if not, tasks from 11 and 21 would mix in with them. I used a minimal amount of additions to act as catch alls, to reduce coding time
\hstop


```{r}
smalldata <- diagnosing_AD_data %>%
  select(starts_with("air"), starts_with("disp"), starts_with("max_x"), starts_with("max_y"), starts_with("num"), starts_with("paper"), starts_with("total"))
```

\hstart
this is the small data, that is showing only the 7 tasks we chose that can be considered accessible. 
\hstop

```{r}

t1 <- smalldata %>%
  select(ends_with("e1"), ends_with("x1"), ends_with("n1"))

t2 <- smalldata %>%
  select(ends_with("e2"), ends_with("x2"), ends_with("n2"))

t3 <- smalldata %>%
  select(ends_with("e3"), ends_with("x3"), ends_with("n3"))

t4 <- smalldata %>%
  select(ends_with("e4"), ends_with("x4"), ends_with("n4"))

t5 <- smalldata %>%
  select(ends_with("e5"), ends_with("x5"), ends_with("n5"))

t6 <- smalldata %>%
  select(ends_with("e6"), ends_with("x6"), ends_with("n6"))

t7 <- smalldata %>%
  select(ends_with("e7"), ends_with("x7"), ends_with("n7"))

t8 <- smalldata %>%
  select(ends_with("e8"), ends_with("x8"), ends_with("n8"))

t9 <- smalldata %>%
  select(ends_with("e9"), ends_with("x9"), ends_with("n9"))

t10 <- smalldata %>%
  select(ends_with("10"))

t11 <- smalldata %>%
  select(ends_with("11"))

t12 <- smalldata %>%
  select(ends_with("12"))

t13 <- smalldata %>%
  select(ends_with("13"))

t14 <- smalldata %>%
  select(ends_with("14"))

t15 <- smalldata %>%
  select(ends_with("15"))

t16 <- smalldata %>%
  select(ends_with("16"))

t17 <- smalldata %>%
  select(ends_with("17"))

t18 <- smalldata %>%
  select(ends_with("18"))

t19 <- smalldata %>%
  select(ends_with("19"))

t20 <- smalldata %>%
  select(ends_with("20"))

t21 <- smalldata %>%
  select(ends_with("21"))

t22 <- smalldata %>%
  select(ends_with("22"))

t23 <- smalldata %>%
  select(ends_with("23"))

t24 <- smalldata %>%
  select(ends_with("24"))

t25 <- smalldata %>%
  select(ends_with("25"))

```


\hstart
this is the small data tasks that we can use for the pairs plots
\hstop

```{r}
pairs(t1)
pairs(t2)
pairs(t3)
pairs(t4)
pairs(t5)
pairs(t6)
pairs(t7)
pairs(t8)
pairs(t9)
pairs(t10)
pairs(t11)
pairs(t12)
pairs(t13)
```

\hstart
1st half of the pairs plots for the small data
\hstop

```{r}
pairs(t14)
pairs(t15)
pairs(t16)
pairs(t17)
pairs(t18)
pairs(t19)
pairs(t20)
pairs(t21)
pairs(t22)
pairs(t23)
pairs(t24)
pairs(t25)
```



