---
title: "Trisha_Script"
author: "Trisha Henderson"
date: "2024-03-04"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr)
library(dplyr) #needed for the %>% function in the data subset loops
library(ggplot2)
#install.packages("GGally")
library("GGally")
library(knitr)
library(xtable)
#install.packages("jtools")
library("jtools")
#install.packages("devtools")
#install.packages("stargazer")
library(stargazer)
```

## R Markdown

```{r}
diagnosing_AD_data <- read_csv("diagnosing_AD_data.csv", show_col_types = FALSE) %>%
  mutate(class = case_when(class == "H" ~ 0,
                           class == "P" ~ 1))

task1 <- diagnosing_AD_data %>%
  select(ends_with("e1"), ends_with("x1"), ends_with("r1"), ends_with("n1"), ends_with("t1"))

task2 <- diagnosing_AD_data %>%
  select(ends_with("e2"), ends_with("x2"), ends_with("r2"), ends_with("n2"), ends_with("t2"))

task3 <- diagnosing_AD_data %>%
  select(ends_with("e3"), ends_with("x3"), ends_with("r3"), ends_with("n3"), ends_with("t3"))

task4 <- diagnosing_AD_data %>%
  select(ends_with("e4"), ends_with("x4"), ends_with("r4"), ends_with("n4"), ends_with("t4"))

task5 <- diagnosing_AD_data %>%
  select(ends_with("e5"), ends_with("x5"), ends_with("r5"), ends_with("n5"), ends_with("t5"))

task6 <- diagnosing_AD_data %>%
  select(ends_with("e6"), ends_with("x6"), ends_with("r6"), ends_with("n6"), ends_with("t6"))

task7 <- diagnosing_AD_data %>%
  select(ends_with("e7"), ends_with("x7"), ends_with("r7"), ends_with("n7"), ends_with("t7"))

task8 <- diagnosing_AD_data %>%
  select(ends_with("e8"), ends_with("x8"), ends_with("r8"), ends_with("n8"), ends_with("t8"))

task9 <- diagnosing_AD_data %>%
  select(ends_with("e9"), ends_with("x9"), ends_with("r9"), ends_with("n9"), ends_with("t9"))

task10 <- diagnosing_AD_data %>%
  select(ends_with("10"))

task11 <- diagnosing_AD_data %>%
  select(ends_with("11"))

task12 <- diagnosing_AD_data %>%
  select(ends_with("12"))

task13 <- diagnosing_AD_data %>%
  select(ends_with("13"))

task14 <- diagnosing_AD_data %>%
  select(ends_with("14"))

task15 <- diagnosing_AD_data %>%
  select(ends_with("15"))

task16 <- diagnosing_AD_data %>%
  select(ends_with("16"))

task17 <- diagnosing_AD_data %>%
  select(ends_with("17"))

task18 <- diagnosing_AD_data %>%
  select(ends_with("18"))

task19 <- diagnosing_AD_data %>%
  select(ends_with("19"))

task20 <- diagnosing_AD_data %>%
  select(ends_with("20"))

task21 <- diagnosing_AD_data %>%
  select(ends_with("21"))

task22 <- diagnosing_AD_data %>%
  select(ends_with("22"))

task23 <- diagnosing_AD_data %>%
  select(ends_with("23"))

task24 <- diagnosing_AD_data %>%
  select(ends_with("24"))

task25 <- diagnosing_AD_data %>%
  select(ends_with("25"))


```

```{r}
H <- which(diagnosing_AD_data$class == "0") 
P <- which(diagnosing_AD_data$class == "1")

n_train_H <- ceiling(0.8 * length(H))
n_train_P <- ceiling(0.8 * length(P))

train_H <- sample(H, size = n_train_H)
train_P <- sample(P, size = n_train_P)

train_both <- c(train_H, train_P)
test <- diagnosing_AD_data[-train_both, ]
diagnosing_AD_data <- diagnosing_AD_data[train_both, ]
```
\hstart
the above is showing the 25 different tasks, using the full data set. the first 9 tasks have additional 'ends with' sections because if not, tasks from 11 and 21 would mix in with them. I used a minimal amount of additions to act as catch alls, to reduce coding time
\hstop

```{r}
ggpairs(task1)
```



```{r}
smalldata <- diagnosing_AD_data %>%
  select(starts_with("air"), starts_with("disp"), starts_with("max_x"), starts_with("max_y"), starts_with("num"), starts_with("paper"), starts_with("total"), starts_with("class"))
```

\hstart
this is the small data, that is showing only the 7 tasks we chose that can be considered accessible. 
\hstop

```{r}

t1 <- smalldata %>%
  select(ends_with("e1"), ends_with("x1"), ends_with("n1"))

t2 <- smalldata %>%
  select(ends_with("e2"), ends_with("x2"), ends_with("n2"))

t3 <- smalldata %>%
  select(ends_with("e3"), ends_with("x3"), ends_with("n3"))

t4 <- smalldata %>%
  select(ends_with("e4"), ends_with("x4"), ends_with("n4"))

t5 <- smalldata %>%
  select(ends_with("e5"), ends_with("x5"), ends_with("n5"))

t6 <- smalldata %>%
  select(ends_with("e6"), ends_with("x6"), ends_with("n6"))

t7 <- smalldata %>%
  select(ends_with("e7"), ends_with("x7"), ends_with("n7"))

t8 <- smalldata %>%
  select(ends_with("e8"), ends_with("x8"), ends_with("n8"))

t9 <- smalldata %>%
  select(ends_with("e9"), ends_with("x9"), ends_with("n9"))

t10 <- smalldata %>%
  select(ends_with("10"))

t11 <- smalldata %>%
  select(ends_with("11"))

t12 <- smalldata %>%
  select(ends_with("12"))

t13 <- smalldata %>%
  select(ends_with("13"))

t14 <- smalldata %>%
  select(ends_with("14"))

t15 <- smalldata %>%
  select(ends_with("15"))

t16 <- smalldata %>%
  select(ends_with("16"))

t17 <- smalldata %>%
  select(ends_with("17"))

t18 <- smalldata %>%
  select(ends_with("18"))

t19 <- smalldata %>%
  select(ends_with("19"))

t20 <- smalldata %>%
  select(ends_with("20"))

t21 <- smalldata %>%
  select(ends_with("21"))

t22 <- smalldata %>%
  select(ends_with("22"))

t23 <- smalldata %>%
  select(ends_with("23"))

t24 <- smalldata %>%
  select(ends_with("24"))

t25 <- smalldata %>%
  select(ends_with("25"))

```


\hstart
this is the small data tasks that we can use for the pairs plots
\hstop

```{r}
pairs(t1) + title("Task 1 Features")
pairs(t2) 
pairs(t3)
pairs(t4)
pairs(t5)
pairs(t6)
pairs(t7)
pairs(t8)
pairs(t9)
pairs(t10)
pairs(t11)
pairs(t12)
pairs(t13)
```

\hstart
1st half of the pairs plots for the small data
\hstop

```{r}
pairs(t14)
pairs(t15)
pairs(t16)
pairs(t17)
pairs(t18)
pairs(t19)
pairs(t20)
pairs(t21)
pairs(t22)
pairs(t23)
pairs(t24)
pairs(t25)
```

\hstart
2nd half of the pairs plots for the small data
\hstop

```{r}
ggpairs(t1, progress = FALSE)
ggpairs(t2, progress = FALSE)
ggpairs(t3, progress = FALSE)
ggpairs(t4, progress = FALSE)
ggpairs(t5, progress = FALSE)
ggpairs(t6, progress = FALSE)
ggpairs(t7, progress = FALSE)
ggpairs(t8, progress = FALSE)
ggpairs(t9, progress = FALSE)
ggpairs(t10, progress = FALSE)
ggpairs(t11, progress = FALSE)
ggpairs(t12, progress = FALSE)
ggpairs(t13, progress = FALSE)
```

\hstart
NICE VERSION of 1st half of the pairs plots for the small data
\hstop

```{r}
ggpairs(t14, progress = FALSE)
ggpairs(t15, progress = FALSE)
ggpairs(t16, progress = FALSE)
ggpairs(t17, progress = FALSE)
ggpairs(t18, progress = FALSE)
ggpairs(t19, progress = FALSE)
ggpairs(t20, progress = FALSE)
ggpairs(t21, progress = FALSE)
ggpairs(t22, progress = FALSE)
ggpairs(t23, progress = FALSE)
ggpairs(t24, progress = FALSE)
ggpairs(t25, progress = FALSE)
```

\hstart
NICE VERSION of 2nd half of the pairs plots for the small data
\hstop

```{r}
g1 <- glm(class ~ air_time1 + paper_time1 + disp_index1 + max_x_extension1 + max_y_extension1 + num_of_pendown1, data = diagnosing_AD_data, family=binomial(link="logit"))
g1


g2 <- glm(class ~ air_time2 + paper_time2 + disp_index2 + max_x_extension2 + max_y_extension2 + num_of_pendown2, data = diagnosing_AD_data, family=binomial(link="logit"))

print(summ(g2,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))

stargazer(g2, type="latex",
          dep.var.labels=c("Miles/(US) gallon","Fast car (=1)"),
          covariate.labels=c("Gross horsepower","Rear axle ratio","Four foward
                             gears", "Five forward gears","Type of transmission
                             (manual=1)"), out="models.htm")

```

\hstart
yay logistic regression model start (NOT the final draft)
\hstop


```{r mylatextable, results = "asis"}
stargazer(g2, type = 'text', out='foo.html', title="Logistic Regression Results for Task 2 Model",covariate.labels=c("Air Time","Paper Time",
"Dispersment Index","Maximum X Extension","Maximum Y Extension","Number of Pendowns"), dep.var.labels=c("Class"), no.space=TRUE, single.row=TRUE)
```


\hstart
1st attempt for table of many. for small data task1
\hstop


```{r}
g1 <- glm(class ~ air_time1 + paper_time1 + disp_index1 + max_x_extension1 + max_y_extension1 + num_of_pendown1, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g1,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g1)

g2 <- glm(class ~ air_time2 + paper_time2 + disp_index2 + max_x_extension2 + max_y_extension2 + num_of_pendown2, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g2,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g2)

g3 <- glm(class ~ air_time3 + paper_time3 + disp_index3 + max_x_extension3 + max_y_extension3 + num_of_pendown3, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g3,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g3)

g4 <- glm(class ~ air_time4 + paper_time4 + disp_index4 + max_x_extension4 + max_y_extension4 + num_of_pendown4, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g4,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g4)

g5 <- glm(class ~ air_time5 + paper_time5 + disp_index5 + max_x_extension5 + max_y_extension5 + num_of_pendown5, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g5,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g5)
```


\hstart
will be using small data for logistic regression - log reg tasks 1 to 5
\hstop


```{r}
g6 <- glm(class ~ air_time6 + paper_time6 + disp_index6 + max_x_extension6 + max_y_extension6 + num_of_pendown6, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g6,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g6)

g7 <- glm(class ~ air_time7 + paper_time7 + disp_index7 + max_x_extension7 + max_y_extension7 + num_of_pendown7, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g7,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g7)

g8 <- glm(class ~ air_time8 + paper_time8 + disp_index8 + max_x_extension8 + max_y_extension8 + num_of_pendown8, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g8,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g8)

g9 <- glm(class ~ air_time9 + paper_time9 + disp_index9 + max_x_extension9 + max_y_extension9 + num_of_pendown9, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g9,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g9)

g10 <- glm(class ~ air_time10 + paper_time10 + disp_index10 + max_x_extension10 + max_y_extension10 + num_of_pendown10, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g10,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g10)
```

\hstart
will be using small data for logistic regression - log reg tasks 6 to 10
\hstop


```{r}
g11 <- glm(class ~ air_time11 + paper_time11 + disp_index11 + max_x_extension11 + max_y_extension11 + num_of_pendown11, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g11,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g11)

g12 <- glm(class ~ air_time12 + paper_time12 + disp_index12 + max_x_extension12 + max_y_extension12 + num_of_pendown12, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g12,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g12)

g13 <- glm(class ~ air_time13 + paper_time13 + disp_index13 + max_x_extension13 + max_y_extension13 + num_of_pendown13, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g13,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g13)

g14 <- glm(class ~ air_time14 + paper_time14 + disp_index14 + max_x_extension14 + max_y_extension14 + num_of_pendown14, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g14,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g14)

g15 <- glm(class ~ air_time15 + paper_time15 + disp_index15 + max_x_extension15 + max_y_extension15 + num_of_pendown15, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g15,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g15)
```

\hstart
will be using small data for logistic regression - log reg tasks 11 to 15
\hstop



```{r}
g16 <- glm(class ~ air_time16 + paper_time16 + disp_index16 + max_x_extension16 + max_y_extension16 + num_of_pendown16, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g16,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g16)

g17 <- glm(class ~ air_time17 + paper_time17 + disp_index17 + max_x_extension17 + max_y_extension17 + num_of_pendown17, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g17,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g17)

g18 <- glm(class ~ air_time18 + paper_time18 + disp_index18 + max_x_extension18 + max_y_extension18 + num_of_pendown18, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g18,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g18)

g19 <- glm(class ~ air_time19 + paper_time19 + disp_index19 + max_x_extension19 + max_y_extension19 + num_of_pendown19, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g19,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g19)

g20 <- glm(class ~ air_time20 + paper_time20 + disp_index20 + max_x_extension20 + max_y_extension20 + num_of_pendown20, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g20,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g20)
```

\hstart
will be using small data for logistic regression - log reg tasks 16 to 20
\hstop


```{r}
g21 <- glm(class ~ air_time21 + paper_time21 + disp_index21 + max_x_extension21 + max_y_extension21 + num_of_pendown21, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g21,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g21)

g22 <- glm(class ~ air_time22 + paper_time22 + disp_index22 + max_x_extension22 + max_y_extension22 + num_of_pendown22, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g22,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g22)

g23 <- glm(class ~ air_time23 + paper_time23 + disp_index23 + max_x_extension23 + max_y_extension23 + num_of_pendown23, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g23,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g23)

g24 <- glm(class ~ air_time24 + paper_time24 + disp_index24 + max_x_extension24 + max_y_extension24 + num_of_pendown24, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g24,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g24)

g25 <- glm(class ~ air_time25 + paper_time25 + disp_index25 + max_x_extension25 + max_y_extension25 + num_of_pendown25, data = diagnosing_AD_data, family=binomial(link="logit"))
print(summ(g25,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g25)
```

\hstart
will be using small data for logistic regression - log reg tasks 20 to 25
\hstop


```{r}
logLik(g1)
logLik(g2)
logLik(g3)
logLik(g4)
logLik(g5)
logLik(g6)
logLik(g7)
logLik(g8)
logLik(g9)
logLik(g10)
logLik(g11)
logLik(g12)
logLik(g13)
logLik(g14)
logLik(g15)
logLik(g16)
logLik(g17)
logLik(g18)
logLik(g19)
logLik(g20)
logLik(g21)
logLik(g22)
logLik(g23)
logLik(g24)
logLik(g25)
```

\hstart
mod 18 is BEST (-109.1087); and mod 15 is WORST (-78.79616)
\hstop

```{r}
train <- subset(diagnosing_AD_data, select = -ID)
test <- subset(test, select = -ID)
```


```{r}
g1a <- glm((class) ~ .,data = train, family=binomial(link="logit"))
print(summ(g1a,model.info=F,digits =4), col.names=c("Estimate", "Standard Error", "Z Value", "P-Value"))
logLik(g1a)
predict(g1a, newdata=test, type="response")

```


```{r}

Mdata <- smalldata %>%
  select(ends_with("1"), ends_with("14"), ends_with("18"), ends_with("20"), ends_with("23"))

full <- glm(class ~ air_time + paper_time + disp_index + max_x_extension + max_y_extension + num_of_pendown, data = Cdata, family=binomial(link="logit"))




```


